Artificial Neural Network based critical conditions for Dynamic Recrystallization of Medium Carbon Steel and Application

### 2023-08-23 Article.tex
semifinal version of the paper

% Abstract (Do not insert blank lines, i.e. \\)
\abstract{\textcolor{red}{The process of dynamic recrystallization is driven by the energy stored in the metal due to plastic deformation. As the metal deforms, the internal energy increases, and at elevated temperatures, atoms have sufficient mobility to rearrange themselves, leading to the formation of new, strain-free, equiaxed grains. These newly formed grains are usually much smaller than the original grains, and their growth is accelerated by the presence of high stored energy and the high temperatures.The process of dynamic recrystallization is driven by the energy stored in the metal due to plastic deformation. As the metal deforms, the internal energy increases, and at elevated temperatures, atoms have sufficient mobility to rearrange themselves, leading to the formation of new, strain-free, equiaxed grains. These newly formed grains are usually much smaller than the original grains, and their growth is accelerated by the presence of high stored energy and the high temperatures.The process of dynamic recrystallization is driven by the energy stored in the metal due to plastic deformation. As the metal deforms, the internal energy increases, and at elevated temperatures, atoms have sufficient mobility to rearrange themselves, leading to the formation of new, strain-free, equiaxed grains. These newly formed grains are usually much smaller than the original grains, and their growth is accelerated by the presence of high stored energy and the high temperatures.}}

% Keywords
\keyword{artificial neural network; constitutive flow law; Gleeble}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{document}

%----------------------------------------------------------------------------------
\section{Introduction\label{sec:Introduction}}
%----------------------------------------------------------------------------------
Dynamic recrystallization (DRX) is a process that occurs in certain materials, especially in metals and alloys, when they undergo plastic deformation (deformation that is not reversible). It is a phenomenon commonly observed during hot working processes like hot rolling, hot forging, or hot extrusion. When a metal or alloy is subjected to high temperatures and significant plastic deformation, the existing grain structure is broken down, and new, smaller grains form in its place and this phenomenon is called DRX. It is different from static recrystallization, which occurs at lower temperatures and takes longer to form new grains. The process of DRX is driven by the energy stored in the metal due to plastic deformation. As the metal deforms, the internal energy increases, and at elevated temperatures, atoms have sufficient mobility to rearrange themselves, leading to the formation of new, strain-free, equiaxed grains. These newly formed grains are usually much smaller than the original grains, and their growth is accelerated by the presence of high stored energy and the high temperatures. DRX offers several advantages during hot working processes in the sense that it helps in refining the grain size, which enhances the mechanical properties of the material, such as strength and toughness. Additionally, it reduces the overall strain energy, which can lead to a more uniform microstructure and improved material properties.

@@

The DRX phenomenon based on inflection point was first studied by Ryan and McQueen \cite{ryan1989dynamic,ryan1990dynamic,ryan1990flow}, who observed the appearance of an inflection point on the curve $\theta=f(\sigma)$ before the peak stress $\sigma_p$ and attributed the beginning of DRX and the critical conditions to this inflection point. Later, Poliak and Jonas \cite{Poliak-1996,ei2003initiation,ei2003critical,jonas2003critical} further demonstrated that this inflection point is associated with the thermodynamic energy released during the movement of dislocations, thus confirming the hypothesis of DRX describing this inflection point; this signifies that an additional softening mechanism begins to operate (in addition to DRC). Najafizadeh and Jonas \cite{najafizadeh2006predicting} simplified the thermodynamic model of Poliak and Jonas by developing an analytical technique, widely used nowadays, to determine the critical conditions for the initiation of DRX. In their approach, they adopted a third-degree polynomial to describe the shape of the curve $\theta=f(\sigma)$ and, by using the second derivative, they identified the critical strain $\varepsilon_c$ and stress $\sigma_c$. Once the critical conditions are calculated, they are considered as input data for the Johnson-Mehl-Avrami-Kolmogorov (JMAK) model \cite{Avrami-1939}, which is widely used to estimate the volumic fraction of DRX ($X_{drx}$) during hot working. Li \eal \cite{li2015experimental} explored the DRX characteristics of micro-alloyed plastic molding steel, using the Avrami kinetics model equation and the Estrin and Mecking mathematical model \cite{estrin1984unified,mecking1981kinetics} to identify all key parameters. Zhang \eal \cite{zhang2016kinetics} studied the DRX behaviors of medium carbon CreNieMo steel alloy using the Avrami kinetics model equation, and qualitatively characterized the metallurgical properties as a function of the Zener-Hollomon parameter. Cho \eal \cite{cho2005prediction} and Razali \eal \cite{razali2021new} predicted the microstructural evolution of Mn alloy (with an emphasis on the DRX and grain growth phenomena) using this well-known model and found that the predicted microstructures were consistent with those revealed by multiple compression tests. The same equation was used by Wan \eal \cite{wan2017experimental} to predict the microstructural evolution of TiAl-based alloys during hot compression. Li \eal \cite{li2018finite} verified the reliability of the Avrami kinetics model equation during compression testing of Inconel 718 bolts. Cui \eal \cite{cui2016hot} investigated DRX using the Avrami
kinetics model equation and showed that the evolution of a $\beta$-solidifying TiAl alloy commonly began at triangular boundaries and only later affected the lamellae.

The accuracy of the critical conditions for DRX is strongly related to how the curve $\theta=f(\sigma)$ is obtained. Indeed, the direct use of raw data from experiments does not provide usable curves. Therefore, commonly used methods involve either smoothing the curve $\sigma=f(\varepsilon)$  as much as possible or approximating this curve with a polynomial function that can reproduce it and deducing the curve $\theta=f(\sigma)$ from it. The disadvantage of these two methods is that they do not always guarantee a good smoothing of the curve $\sigma=f(\varepsilon)$. However, an Artifical Neural Networks (ANN) method is a universal approximator that has proven its effectiveness in several fields, including predicting the material's flow behavior. Based on this tool, we propose, in this study, to replace the two smoothing methods with an ANN to obtain the critical conditions for DRX. In other words, the proposed approach suggests using an ANN to model the relationship between the stress ($\sigma$) and the rate hardening ($\theta$) directly, avoiding the need for explicit smoothing of experimental data. By training the ANN with appropriate data, it can learn the underlying relationship between stress and DRX, thus providing a more accurate estimation of the critical conditions for DRX. \textcolor{red}{Using ANN in materials science and engineering has gained popularity due to their ability to learn complex patterns and relationships from data, making them valuable tools for various predictions and analyses in the field. By leveraging a ANN in this context, researchers aim to improve the accuracy and reliability of predictions related to DRX behavior in materials during deformation}.

%----------------------------------------------------------------------------------
\section{Materials and experiments\label{sec:MaterialsExperiments}}
%----------------------------------------------------------------------------------
The experimental tests on which this work is based are strictly identical to those already published by Tize Mha \eal \cite{TizeMha-2023}.
For further information, readers may refer to this other publication by our research group. We will, however, list here-after the main points required to understand the proposed approach. The first publication focused on developing a constitutive law capable of predicting material flow, for which a comparative study between 5 analytical models and a neural network-based model was conducted. At the conclusion of this comparative study, the Artificial Neural Network (ANN) model proved to be the best performing. In this new study, the ANN model will be utilized for predicting dynamic recrystallization, as explained in the introduction. It's worth noting that the ANN model identified in the first publication will also be employed for managing the plastic behavior of the material.\OP{Already done}

@@

To get around this problem, some authors recommend smoothing the experimental data (using the Excel solver for \cite{Najafizadeh-2006}) or identifying an analytical form (e.g. a polynomial of relatively high order) using a minimization algorithm.
But, depending on the degree of the polynomial and for the same stress/strain curve, several solutions can be obtained, leading to the definition of several possible forms for the $\theta(\sigma)$ function.

@@

\begin{table}[h!]
\caption{Critical conditions based on Poliak and Jonas model  \cite{najafizadeh2006predicting}.}\vspace{-5mm}
\begin{center}
\begin{tabular}{cccccc}
\toprule
$\mdot{\varepsilon}~~(\text{s}^{-1})$ & $T$ ($^\circ$C) & $\varepsilon_p$ & $\sigma_p$ (MPa)& $\varepsilon_c$ & $\sigma_c$ (MPa) \\
\hline
         & $1050$  & $0.178$  & $37.862$& $0.083$ & $33.050$ \\
& $1100$ & $0.143$ & $29.770$ & $0.067$ & $25.648$ \\
$0.001$  & $1150$  & $0.124$  & $23.330$& $0.051$ & $19.116$ \\
& $1200$ & $0.102$ & $19.373$ & $0.039$ & $16.244$ \\
& $1250$ & $0.084$ & $13.883$ & $0.035$ & $11.302$ \\

@@

& $1050$ & $0.700$ & $127.172$&$0.577$ /&$116.1$ / \\ 
& $1100$ & $0.700$ & $106.608$& $0.329$/& $94.51$/ \\
$1$      & $1150$  & $0.700$  & $89.525$& $0.668$ & $89.067$ \\
& $1200$ & $0.700$ & $72.270$ & $0.178$ & $57.929$ \\
& $1250$ & $0.393$ & $59.992$ & $0.112$ & $54.066$ \\
\bottomrule
\end{tabular}	
\end{center}
\label{tab:OPparams}
\end{table}

@@

The calculation of the parameters of JMAK model involves two main steps. Firstly, it entails determining the coefficients $A_{c,p}, n_{c,p}, B_{c,p,s}$ and $m_{c,p,s}$. Secondly, these coefficients are then incorporated into equation (\ref{eq:paramsZ}) for their final use in equations (\ref{eq:drxpred}) and (\ref{eq:drxexp}).To compute these parameters, a Python code using the $curve\_fitting$ method is used. Specifically, the critical strains and stresses calculated in the previous sections are used as input data for these parameter identifications. The curve fitting method aims to find the best-fitting values for the coefficients by iteratively adjusting them to minimize the difference between the predicted and experimental critical strains and stresses. This optimization process involves trying various combinations of the coefficients and evaluating their fitness to the given data. The curve fitting technique adjusts the coefficients until it achieves the closest match between the model's predictions and the experimental values.

@@

\begin{table}[h]
%\centering{}
\caption{JMAK model and Zener-Hollomon dependency parameters }\vspace{-1mm}
\begin{tabular}{cc}
\toprule
Parameters & Values  \\
\hline
$A_c$&$4.4268\times10^{-5}	$\\
$A_p$&$29.85\times10^{-5}$\\
$B_c$&$0.0720627$\\
$B_p$&$0.103141	$\\
$B_s$&$10265.8	$\\
$n_c$&$0.235832	$\\
$n_p$&$0.203678	$\\
$m_c$&$0.188236	$\\
$m_p$&$0.181822	$\\
$m_s$&$-0.19708	$\\
$k$  &$0.48632	$\\
$n_k$&$3.36531$ \\
\bottomrule
\end{tabular}	
\label{tab:allparams}
\end{table}

@@

%----------------------------------------------------------------------------------
\section{Numerical simulation of the compression\label{sec:NumSim}}
%----------------------------------------------------------------------------------
In this section, the numerical validation of the previously performed dynamic recrystallization identification will be addressed. To achieve this, it is essential to establish a constitutive law capable of accurately predicting the plastic deformation of this particular material. In our prior publication, a comparison between analytical constitutive laws and neural network-based approaches was conducted, resulting in the identification of an ANN model as the suitable choice for this material. As a result, this section comprises a two-fold focus: firstly, a recapitulation of the constitutive law identification, as presented in the previous article; and secondly, the integration of this identified ANN model with the JMAK model for predicting dynamic recrystallization behaviour.
%----------------------------------------------------------------------------------
\subsection{Identification of the ANN constitutive law\label{subsec:ANNConstitutiveLaw}}
%----------------------------------------------------------------------------------
In general terms, flow stress $\sigma$ is a non-linear function of the strain $\varepsilon$, increasing with the strain rate $\mdot\varepsilon$, but decreasing with increasing temperature $T$.
The model can therefore be described as an elastoplastic model with the influence of strain rate and temperature.
This type of behavior generally leads to Johnson-Cook \cite{Johnson-1983}, Zerilli Armstrong \cite{Zerilli-1987}, Hansel Spittle \cite{Hensel-1978} or Arrhenius \cite{Sellars-1966} flow law type.
Depending on the nature of the stress-strain relationship, modeling with one or other of these models can take into account the actual behavior of the material at certain strain rates.
As reported by Tize Mha \eal \cite{TizeMha-2023}, Johnson-Cook, Zerilli Armstrong or Hansel Spittle type models, while providing a more or less faithful reproduction of material behavior at strain rates above $1~\ps$, do not take into account the softening due to DRX visible on experimental curves for strain rates below $1~\ps$ as reported in Figure  \ref{fig:RawData}.
Indeed, for the lowest strain rates, the flow stress $\sigma$ increases with strain $\varepsilon$ up to a value of around $\varepsilon=0.2$ to $0.3$ and then decreases to maintain a more or less constant value until the end of the test.
Only the Arrhenius model can more or less account for this softening at low strain rates.
As proposed by Pantalé \eal \cite{Pantale-2021, Pantale-2023} and Tize Mha \eal \cite{TizeMha-2023}, an effective alternative is to use a flow law defined by an artificial neural network trained directly on experimental data from compression tests.
Correctly defining the hyperparameters of this neural network (number of hidden layers, number of neurons, activation functions, etc.) allows us to obtain a flow law that faithfully reproduces the data obtained from compression tests.

@@

\begin{figure}[H]
%\centering
\includegraphics[width=0.7\columnwidth]{Figures/ANN-scheme-2HL}
\caption{Two hidden layers artificial neural network architecture with 3 inputs neurons (green) and 1 output neuron (red).}
\label{fig:ANN-2HL}
\end{figure}

@@

\begin{table}[H]
\caption{Architecture and accuracy coefficients for all the proposed networks.}
\newcolumntype{C}{>{\centering\arraybackslash}X}
\newcolumntype{L}{>{\raggedright\arraybackslash}X}
\begin{tabularx}{\textwidth}{LCCCCCC}
\hline
\textbf{Coefficients} & \textbf{3-7-5-1} & \textbf{3-9-4-1} & \textbf{3-9-5-1} & \textbf{3-9-7-1} & \textbf{3-13-7-1} & \textbf{3-15-7-1} \\
\hline
$N_{int}$ & $74$ & $81$ & $92$ & $114$ & $158$ &$180$\\
\hline
$\log_{10}(\RMSE)$ & $-2.40$ & $-2.42$ & $-2.38$ & $-2.45$ & $-2.50$ & $-2.58$ \\
$\MARE(\%)$ & $1.13$ & $1.05$ & $1.08$ & $0.91$ & $0.75$ & $0.62$ \\
$\RMSE(\MPa)$ & $0.59$ & $0.57$ & $0.65$ & $0.55$ & $0.46$ & $0.38$ \\
\hline
\end{tabularx}
\label{tab:Errors}
\end{table}

@@

%----------------------------------------------------------------------------------
\subsection{DRX simulation\label{subsec:DRXSimulation}}
In order to assess the effectiveness of the implementation of the model presented in the previous sections, a compression test is simulated in this section. For this purpose, the material used for this simulation is a medium-carbon P20 iron alloy, which was used for the identification of this model. An axisymmetric Finite Element Method (FEM) model of hot cylinder compression with a height of $15$ mm and a diameter of $5$ mm is used, as shown in Figure \ref{fig:Mesh}. The frictional coefficient at the material/Die interface was assumed to be $0.2$ \cite{zhang2019elevated,sun2020kinetique}. The mesh consists of 986 CAX4R elements (4-node axisymmetric bi-linear quadrilateral elements with reduced integration and hourglass control). The FEM model is simulated using Abaqus/Implicit due to the computation time caused by the low strain rates. A displacement of $60\%, ~45\%, ~30\%$ and $15\%$ mm of the total height is imposed on the upper part of the cylinder during the compression along the vertical axis of the specimen. The radial displacement $u_r$ of the upper part of the specimen is left free, while its axial displacement $u_z$ is imposed. The lower part of the cylinder remains fixed during the simulation. The effect of reducing the cylinder in combination with strain rate or temperature effect has been also evaluated in this simulation, and conclusions have been drawn. For this simulation, three temperatures ($1050^\circ$C, $1150^\circ$C, and $1250^\circ$C) and four strain rates ($0.001~\text{s}^{-1}$, $0.01~\text{s}^{-1}$, $0.1~\text{s}^{-1}$ and $1.0~\text{s}^{-1}$) are considered.
\begin{figure}[H]
%\centering
\includegraphics[width=0.6\columnwidth]{Figures/CyCompression2}
\caption{Numerical model for the compression test}
\label{fig:Mesh}
\end{figure}

%----------------------------------------------------------------------------------
\subsubsection{Temperature effect on DRX distribution\label{subsec:TempEffect}}
%----------------------------------------------------------------------------------
\begin{figure}[H]
%\centering
\includegraphics[width=0.98\columnwidth]{Figures/Temp_DRX}
\caption{$X_{drx}$ values at a strain rate of $0.01~\text{s}^{-1}$ for different reductions and initial temperatures.}
\label{fig:TempEffect}
\end{figure}
%----------------------------------------------------------------------------------
\subsubsection{Strain rate effect on DRX distribution\label{subsec:SRatEffect}}
%----------------------------------------------------------------------------------
\begin{figure}[H]
%\centering
\includegraphics[width=0.98\columnwidth]{Figures/SR_DRX}
\caption{$X_{drx}$ values at a fixed $T_0=1150^\circ$C for different reductions and strain rates.}
\label{fig:SREffect}
\end{figure}
%----------------------------------------------------------------------------------
\section{Conclusions\label{sec:Conclusions}}
%----------------------------------------------------------------------------------

>>>>

% Abstract (Do not insert blank lines, i.e. \\)
\abstract{This study presents a novel and comprehensive approach for understanding and simulating the dynamic recrystallization (DRX) process during hot compression. To achieve this, the high-temperature deformation behavior of a medium carbon steel was studied over a wide range of strains, strain rates, and temperatures using hot compression tests on a Gleeble-3800 and ANN based flow behaviour law was used to model the plastic behaviour. The accuracy of the DRX volumic fraction, both during its identification using analytical models and its numerical implementation in finite element software, relies on critical conditions and therfore, in this study, an artificial neural network, as a universal approximator, is proposed to fit the necessary data for calculating the critical conditions of DRX. The JMAK model was used as an analytical model to calculate the volumic fraction of DRX, and its validation against experimental data was successful. A numerical implementation of the Johnson-Mehl-Avrami-Kohnogorov (JMAK) model was implemented into ABAQUS software, and the obtained results were compared with experimental data through microstructure analysis, revealing a strong correlation between simulation and experimentation. Temperature, strain rate and the amount of deformation effects on DRX evoultion were also investigated in this study and it was observed that the DRX rises with temperature and deformation while it decreases with the increase of strain rates.
}

% Keywords
\keyword{Artificial Neural Network; Constitutive Flow Law; Gleeble simulator, Dynamic Recrystallization, Finite Element Analysis}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{document}
%----------------------------------------------------------------------------------
\section{Introduction\label{sec:Introduction}}
%----------------------------------------------------------------------------------
Dynamic recrystallization (DRX) is a process that occurs in certain materials, especially in metals and alloys, when they undergo plastic deformation (deformation that is not reversible). It is a phenomenon commonly observed during hot working processes like hot rolling, hot forging, or hot extrusion. When a metal or alloy is subjected to high temperatures and significant plastic deformation, the existing grain structure is broken down, and new, smaller grains form in its place and this phenomenon is called DRX. It is different from static recrystallization, which occurs at lower temperatures and takes longer to form new grains. The process of DRX is driven by the energy stored in the metal due to plastic deformation. As the metal deforms, the internal energy increases, and at elevated temperatures, atoms have sufficient mobility to rearrange themselves, leading to the formation of new, strain-free, equiaxed grains. These newly formed grains are usually much smaller than the original grains, and their growth is accelerated by the presence of high stored energy and the high temperatures. DRX offers several advantages during hot working processes in the sense that it helps in refining the grain size, which enhances the mechanical properties of the material, such as strength and toughness. Additionally, it reduces the overall strain energy, which can lead to a more uniform microstructure and improved material properties.

@@

The DRX phenomenon based on inflection point was first studied by Ryan and McQueen \cite{ryan1989dynamic,ryan1990dynamic,ryan1990flow}, who observed the appearance of an inflection point on the curve $\theta=f(\sigma)$ before the peak stress $\sigma_p$ and attributed the beginning of DRX and the critical conditions to this inflection point. Later, Poliak and Jonas \cite{Poliak-1996,ei2003initiation,ei2003critical,jonas2003critical} further demonstrated that this inflection point is associated with the thermodynamic energy released during the movement of dislocations, thus confirming the hypothesis of DRX describing this inflection point; this signifies that an additional softening mechanism begins to operate (in addition to DRC). Najafizadeh and Jonas \cite{najafizadeh2006predicting} simplified the thermodynamic model of Poliak and Jonas by developing an analytical technique, widely used nowadays, to determine the critical conditions for the initiation of DRX. In their approach, they adopted a third-degree polynomial to describe the shape of the curve $\theta=f(\sigma)$ and, by using the second derivative, they identified the critical strain $\varepsilon_c$ and stress $\sigma_c$. Once the critical conditions are calculated, they are considered as input data for the Johnson-Mehl-Avrami-Kolmogorov (JMAK) model \cite{Avrami-1939}, which is widely used to estimate the volumic fraction of DRX ($X_{drx}$) during hot working. Li \eal \cite{li2015experimental} explored the DRX characteristics of micro-alloyed plastic molding steel, using the Avrami kinetics model equation and the Estrin and Mecking mathematical model \cite{estrin1984unified,mecking1981kinetics} to identify all key parameters. Zhang \eal \cite{zhang2016kinetics} studied the DRX behaviors of medium carbon CreNieMo steel alloy using the Avrami kinetics model equation, and qualitatively characterized the metallurgical properties as a function of the Zener-Hollomon parameter. Cho \eal \cite{cho2005prediction} and Razali \eal \cite{razali2021new} predicted the microstructural evolution of Mn alloy (with an emphasis on the DRX and grain growth phenomena) using this well-known model and found that the predicted microstructures were consistent with those revealed by multiple compression tests. The same equation was used by Wan \eal \cite{wan2017experimental} to predict the microstructural evolution of TiAl-based alloys during hot compression. Li \eal \cite{li2018finite} verified the reliability of the Avrami kinetics model equation during compression testing of Inconel 718 bolts. Cui \eal \cite{cui2016hot} investigated DRX using the Avrami kinetics model equation and showed that the evolution of a $\beta$-solidifying TiAl alloy commonly began at triangular boundaries and only later affected the lamellae. Recently, Chen \eal \cite{chen2023finite} performed Finite Element Analysis of DRX based on GCr15 microstruture analysis and observed that temperature, strain rate have important effect on the DRX initiation.

The accuracy of the critical conditions for DRX is strongly related to how the curve $\theta=f(\sigma)$ is obtained. Indeed, the direct use of raw data from experiments does not provide usable curves. Therefore, commonly used methods involve either smoothing the curve $\sigma=f(\varepsilon)$  as much as possible or approximating this curve with a polynomial function that can reproduce it and deducing the curve $\theta=f(\sigma)$ from it. The disadvantage of these two methods is that they do not always guarantee a good smoothing of the curve $\sigma=f(\varepsilon)$. However, an Artifical Neural Networks (ANN) method is a universal approximator that has proven its effectiveness in several fields, including predicting the material's flow behavior. Based on this tool, we propose, in this study, to replace the two smoothing methods with an ANN to obtain the critical conditions for DRX. In other words, the proposed approach suggests using an ANN to model the relationship between the stress ($\sigma$) and the rate hardening ($\theta$) directly, avoiding the need for explicit smoothing of experimental data. By training the ANN with appropriate data, it can learn the underlying relationship between stress and DRX, thus providing a more accurate estimation of the critical conditions for DRX.

%----------------------------------------------------------------------------------
\section{Materials and experiments\label{sec:MaterialsExperiments}}
%----------------------------------------------------------------------------------
The experimental tests on which this work is based are strictly identical to those already published by Tize Mha \eal \cite{TizeMha-2023}.
For further information, readers may refer to this other publication by our research group. We will, however, list here-after the main points required to understand the proposed approach. The first publication focused on developing a constitutive law capable of predicting material flow, for which a comparative study between 5 analytical models and a neural network-based model was conducted. At the conclusion of this comparative study, the Artificial Neural Network (ANN) model proved to be the best performing. In this new study, the ANN model will be utilized for predicting dynamic recrystallization, as explained in the introduction. It's worth noting that the ANN model identified in the first publication will also be employed for managing the plastic behavior of the material.

@@

To get around this problem, some authors recommend smoothing the experimental data (using the Excel solver for example \cite{Najafizadeh-2006}) or identifying an analytical form (e.g. a polynomial of relatively high order) using a minimization algorithm.
But, depending on the degree of the polynomial and for the same stress/strain curve, several solutions can be obtained, leading to the definition of several possible forms for the $\theta(\sigma)$ function.

@@

\begin{table}[h!]
%\centering
\caption{Critical conditions based on Poliak and Jonas model  \cite{najafizadeh2006predicting}.}\vspace{-1mm}
\begin{tabular}{cccccc}
\toprule
$\mdot{\varepsilon}~~(\text{s}^{-1})$ & $T$ ($^\circ$C) & $\varepsilon_p$ & $\sigma_p$ (MPa)& $\varepsilon_c$ & $\sigma_c$ (MPa) \\
\hline
         & $1050$  & $0.178$  & $37.862$& $0.083$ & $33.050$ \\
& $1100$ & $0.143$ & $29.770$ & $0.067$ & $25.648$ \\
$0.001$  & $1150$  & $0.124$  & $23.330$& $0.051$ & $19.116$ \\
& $1200$ & $0.102$ & $19.373$ & $0.039$ & $16.244$ \\
& $1250$ & $0.084$ & $13.883$ & $0.035$ & $11.302$ \\

@@

& $1050$ & $0.700$ & $127.172$&$0.577$  &$116.1$  \\ 
& $1100$ & $0.700$ & $106.608$& $0.329$ & $94.51$ \\
$1$      & $1150$  & $0.700$  & $89.525$& $0.268$ & $89.067$ \\
& $1200$ & $0.700$ & $72.270$ & $0.178$ & $57.929$ \\
& $1250$ & $0.393$ & $59.992$ & $0.112$ & $54.066$ \\
\bottomrule
\end{tabular}	
\label{tab:OPparams}
\end{table}

@@

The calculation of the parameters of JMAK model involves two main steps. Firstly, it entails determining the coefficients $A_{c,p}, n_{c,p}, B_{c,p,s}$ and $m_{c,p,s}$. Secondly, these coefficients are then incorporated into equation (\ref{eq:paramsZ}) for their final use in equations (\ref{eq:drxpred}) and (\ref{eq:drxexp}). To compute these parameters, a Python code using the $curve\_fitting$ method is used. Specifically, the critical strains and stresses calculated in the previous sections are used as input data for these parameter identifications. The curve fitting method aims to find the best-fitting values for the coefficients by iteratively adjusting them to minimize the difference between the predicted and experimental critical strains and stresses. This optimization process involves trying various combinations of the coefficients and evaluating their fitness to the given data. The curve fitting technique adjusts the coefficients until it achieves the closest match between the model's predictions and the experimental values.

@@

\begin{table}[h]
%\centering{}
\caption{JMAK model and Zener-Hollomon dependency parameters }\vspace{-1mm}
\begin{tabular}{cccccc}
\toprule
$A_c$ & $A_p$& $B_c$&  $B_p$& $B_s$& $n_c$ \\
\hline
$4.4268\times10^{-5}$& $29.85\times10^{-5}$& $0.0720627$&$0.103141	$&$10265.8	$&$0.235832	$\\
\toprule
$n_p$ & $m_c$& $m_p$&  $m_s$& $k$& $n_k$ \\
\hline
$0.203678	$& $0.188236$&$0.181822$&$-0.19708$&$0.48632$&$3.36531$\\
\bottomrule
\end{tabular}	
\label{tab:allparams}
\end{table}

@@

%----------------------------------------------------------------------------------
\section{Numerical simulation of the compression\label{sec:NumSim}}
%----------------------------------------------------------------------------------
In this section, the numerical validation of the previously performed dynamic recrystallization identification will be addressed. To achieve this, it is essential to establish a constitutive law capable of accurately predicting the plastic deformation of the material. In our prior publication (Tize Mha \eal \cite{TizeMha-2023}), a comparison between analytical constitutive laws and neural network based approache was conducted, resulting in the identification of an ANN model as the suitable choice for this material. As a result, this section comprises a two-fold focus: firstly, a recapitulation of the ANN based constitutive law identification, as presented in the previous article; and secondly, the integration of this identified ANN model with the JMAK model for predicting dynamic recrystallization behaviour.
%----------------------------------------------------------------------------------
\subsection{Identification of the ANN constitutive law\label{subsec:ANNConstitutiveLaw}}
%----------------------------------------------------------------------------------
In general terms, flow stress $\sigma$ is a non-linear function of the strain $\varepsilon$, increasing with the strain rate $\mdot\varepsilon$, but decreasing with increasing temperature $T$.
The model can therefore be described as an elastoplastic model with the influence of strain rate and temperature.
This type of behavior generally leads to Johnson-Cook \cite{Johnson-1983}, Zerilli Armstrong \cite{Zerilli-1987}, Hansel Spittle \cite{Hensel-1978} or Arrhenius \cite{Sellars-1966} flow law type.
Depending on the nature of the stress-strain relationship, modeling with one or other of these models can take into account the actual behavior of the material at certain strain rates.
As reported by Tize Mha \eal \cite{TizeMha-2023}, Johnson-Cook, Zerilli Armstrong or Hansel Spittle type models, while providing a more or less faithful reproduction of material behavior at strain rates above $1~\ps$, do not take into account the softening due to DRX visible on experimental curves for strain rates below $1~\ps$ as reported in Figure  \ref{fig:RawData}.
Indeed, for the lowest strain rates, the flow stress $\sigma$ increases with strain $\varepsilon$ up to a value of around $\varepsilon=0.2$ to $0.3$ and then decreases to maintain a more or less constant value until the end of the test.
Only the Arrhenius model can more or less account for this softening at low strain rates.
As proposed by Pantalé \eal \cite{Pantale-2021, Pantale-2023} and Tize Mha \eal \cite{TizeMha-2023}, an effective alternative is to use a flow law defined by an artificial neural network trained directly on experimental data from compression tests.
Correctly defining the hyperparameters of this neural network (number of hidden layers, number of neurons, activation functions, etc.) allows us to obtain a flow law that faithfully reproduces the data obtained from compression tests.

@@

\begin{figure}[H]
%\centering
\includegraphics[width=0.55\columnwidth]{Figures/ANN-scheme-2HL}
\caption{Two hidden layers artificial neural network architecture with 3 inputs neurons (green) and 1 output neuron (red).}
\label{fig:ANN-2HL}
\end{figure}

@@

\begin{table}[H]
\caption{Architecture and accuracy coefficients for all the proposed networks.}
\newcolumntype{C}{>{\centering\arraybackslash}X}
\newcolumntype{L}{>{\raggedright\arraybackslash}X}
\begin{tabularx}{\textwidth}{LCCCCCC}
\toprule
\textbf{Coefficients} & \textbf{3-7-5-1} & \textbf{3-9-4-1} & \textbf{3-9-5-1} & \textbf{3-9-7-1} & \textbf{3-13-7-1} & \textbf{3-15-7-1} \\
\hline
$N_{int}$ & $74$ & $81$ & $92$ & $114$ & $158$ &$180$\\
\toprule
$\log_{10}(\RMSE)$ & $-2.40$ & $-2.42$ & $-2.38$ & $-2.45$ & $-2.50$ & $-2.58$ \\
$\MARE(\%)$ & $1.13$ & $1.05$ & $1.08$ & $0.91$ & $0.75$ & $0.62$ \\
$\RMSE(\MPa)$ & $0.59$ & $0.57$ & $0.65$ & $0.55$ & $0.46$ & $0.38$ \\
\bottomrule
\end{tabularx}
\label{tab:Errors}
\end{table}

@@

%----------------------------------------------------------------------------------
\subsection{Dynamic recrystallization simulation\label{subsec:DRXSimulation}}
%----------------------------------------------------------------------------------
In order to assess the effectiveness of the implementation of the DRX model presented in the previous sections, a compression test is simulated in this section. For this purpose, the material used for this simulation is a medium-carbon P20 iron alloy, which was used for the identification of this model. An axisymmetric Finite Element Method (FEM) model of hot cylinder compression with a height of $15$ mm and a diameter of $5$ mm is used, as shown in Figure \ref{fig:Mesh}. The frictional coefficient at the material/Die interface was assumed to be $0.2$ \cite{zhang2019elevated,sun2020kinetique}. The mesh consists of 986 CAX4R elements (4-node axisymmetric bi-linear quadrilateral elements with reduced integration and hourglass control). The FEM model is simulated using Abaqus/Implicit due to the computation time related to the low strain rates. A displacement of $60\%, ~45\%, ~30\%$ and $15\%$ mm of the total height is imposed on the upper part of the cylinder during the compression along the vertical axis of the specimen. The radial displacement $u_r$ of the upper part of the specimen is left free, while its axial displacement $u_z$ is imposed. The lower part of the cylinder remains fixed during the simulation. The effect of reducing the cylinder in combination with strain rate and temperature effect has been also evaluated in this simulation, and conclusions have been drawn. For this simulation, three temperatures ($1050^\circ$C, $1150^\circ$C, and $1250^\circ$C) and four strain rates ($0.001~\text{s}^{-1}$, $0.01~\text{s}^{-1}$, $0.1~\text{s}^{-1}$ and $1.0~\text{s}^{-1}$) are considered.
\begin{figure}[H]
%\centering
\includegraphics[width=0.6\columnwidth]{Figures/CyCompression2}
\caption{Numerical model for the compression test}
\label{fig:Mesh}
\end{figure}

%----------------------------------------------------------------------------------
\subsubsection{Temperature and strain rate effects \label{subsec:TempSReffect}}
%----------------------------------------------------------------------------------

Temperature and strain rate play a crucial role in influencing dynamic recrystallization in materials, particularly for metals and alloys in the sense that they lead to the formation of new grains within the material. Indeed, higher temperature and low strain rate generally lead to increased nucleation rates and faster growth rates of new grains during dynamic recrystallization while in opposite lower temperature and higher strain rate lead to imcomplete dynamic recrystallization. At elevated temperatures, the mobility of atoms and dislocations is enhanced, allowing for the creation of new grain boundaries and the growth of new grains. This results in a finer and more equiaxed grain structure. Also, higher temperatures can lead to a higher fraction of recrystallized material because the enhanced mobility of dislocations promotes the formation of new grains. This can result in a significant change in the microstructure and mechanical properties of the material. Figure \ref{fig:TempEffect} and Figure \ref{fig:SREffect} illustrate the simulated results of the DRX fraction of P20 steel under varying deformation conditions. Figure \ref{fig:TempEffect} illustrates that as the temperature rises, the scope of dynamic recrystallization expands. The gradual rise in the dynamic recrystallization fraction within the center is evident, spreading outward. This expansion is attributed to heightened thermal activation and increased atomic diffusion at elevated temperatures, rendering the material more susceptible to dynamic recrystallization. The $X_{drx}$ clearly increases with increasing temperature and reduction. At $45\%$ and $60\%$ reduction, the $X_{drx}$ of P20 steel
reached $100\%$ in the central part of the specimen for all the initial sample temperatures. Indeed, the plastic deformation of a material is accompanied by the creation of dislocations. These dislocations represent a "store of elastic energy". When the temperature is high enough, the dislocations become spontaneously mobile and cause a reorganisation of the crystal structure, in two stages: restoration and recrystallisation. The nature of the phases does not change (those that are thermodynamically stable), the atoms keep the same lattice, but the grain boundaries and the orientation of the crystallites change.
